Distance Sampling in \proglang{R}

### 2016-03-20 paper.Rmd
getting bored of messing with these plots

```{r adjust-mix-comp, fig.width=10, fig.height=3, fig.cap="Possible (though not necessarily plausible) shapes for the detection function when adjustments are included for half-normal and hazard-rate models.\\label{fig:keyadj}", echo=FALSE}
par(mfrow=c(1,4), mar=c(3.5, 3, 3, 1) + 0.1)

## half-normal with cosine
g <- function(x) exp(-x^2/(2*0.01^2))*(1+0.5*cos((2*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Half-normal with \n1 cosine adjustment", xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)
# 2 cosines
g <- function(x) exp(-x^2/(2*0.01^2))*(1-0.06*cos((2*pi*x)/0.025)+0.25*cos((3*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Half-normal with \n2 cosine adjustments",xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)

## hazard-rate with cosine
g <- function(x) (1 - exp(-(x/0.005)^-1.1))*(1-0.05*cos((2*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Hazard-rate with \n1 cosine adjustment", xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)
# 2 cosines
g <- function(x) (1 - exp(-(x/0.005)^-1.9))*
                  (1+0.05*cos((2*pi*x)/0.025) + 0.25*cos((3*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Hazard-rate with \n2 cosine adjustments", xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)
```

>>>>

```{r adjust-mix-comp, fig.width=10, fig.height=3, fig.cap="Possible shapes for the detection function when cosine adjustments are included for half-normal and hazard-rate models.\\label{fig:keyadj}", echo=FALSE}
par(mfrow=c(1,4), mar=c(3.5, 3, 3, 1) + 0.1)

## half-normal with cosine
g <- function(x) exp(-x^2/(2*0.01^2))*(1+0.5*cos((2*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Half-normal with \n1 cosine adjustment", xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)
# 2 cosines
g <- function(x) exp(-x^2/(2*0.011^2))*(1-0.06*cos((2*pi*x)/0.025)+0.25*cos((3*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Half-normal with \n2 cosine adjustments",xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)

## hazard-rate with cosine
g <- function(x) (1 - exp(-(x/0.011)^-3))*(1+0.05*cos((2*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Hazard-rate with \n1 cosine adjustment", xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)
# 2 cosines
g <- function(x) (1 - exp(-(x/0.0199)^-1.4))*
                 (1-0.08*cos((2*pi*x)/0.025)+0.08*cos((3*pi*x)/0.025))
f <- function(x) g(x)/g(0)
curve(f, from=0, to=0.025, xlab="", ylab="", main="Hazard-rate with \n2 cosine adjustment", xlim=c(0,0.025), ylim=c(0,1))
title(xlab="Distance", line=2)
title(ylab="Detection probability", line=2)
```
